Tight battle between republicans and democrats with Kamala in the lead

### 2024-11-05 paper/paper.qmd
Cleaned figure 5 and 6
Too many subplots, limited to 13 pollsters to ensure that readers are able to get a generalised idea per plot

According to @tbl-transscore_harris and @tbl-transscore_trump, the difference between candidates is very minimal, with the minimum, maximum, and even average being the same (only in the media do we see a slight lead by Trump). Both @fig-transscore_harris & @fig-transscore_trump are similar as well, with most polls achieving a 9.0 transparency score.
```{r}
#| label: fig-transscore_harris
#| fig-cap: As election day draws close, pollsters are wrapping up their polls and posting their predictions on who will win. The polls in this graph predict Harris' win percentage, with the average in the blue line. The dots in the graph below represent individual polls conducted in the months leading up to the election. They are coloured based on their transparency_score, which is fivethirtyeight's metric for transpareny in the pollster's methodology. 
#| echo: false
#| warning: false
#| message: false

@@

@@

# Color by transparency_score
base_plot_trump +
  geom_point(aes(color = factor(numeric_grade))) +
  geom_smooth(color = "red") +
  theme(legend.position = "bottom")
```

@@

### `pollster`

@@

@fig-pollster_harris & @fig-pollster_trump show an interesting bump in predictions by George Mass. This may have been an error on their part however, as it is almost immediately rectified.
```{r}
#| label: fig-pollster_harris
#| fig-cap: As election day draws close, pollsters are wrapping up their polls and posting their predictions on who will win. Each graph shows individual polls conducted in the months leading up to the election. They represent the change in prediciton for Kamala Harris winning the presidency.
#| echo: false
#| warning: false
#| message: false

# Facet by pollster
base_plot_kamala +
  geom_point() +
  geom_smooth(color = "blue") +
  facet_wrap(vars(pollster))
```
```{r}
#| label: fig-pollster_trump
#| fig-cap: As election day draws close, pollsters are wrapping up their polls and posting their predictions on who will win. Each graph shows individual polls conducted in the months leading up to the election. They represent the change in prediciton for Donald Trump winning the presidency.  
#| echo: false
#| warning: false
#| message: false

# Facet by pollster
base_plot_trump +
  geom_point() +
  geom_smooth(color = "red") +
  facet_wrap(vars(pollster))
```

>>>>

According to @tbl-transscore_trump and @tbl-transscore_harris, the difference between candidates is very minimal, with the minimum, maximum, and even average being the same (only in the media do we see a slight lead by Trump). Both @fig-transscore_trump and @fig-transscore_harris are similar as well, with most polls achieving a 9.0 transparency score.

@@

```{r}
#| label: fig-transscore_harris
#| fig-cap: As election day draws close, pollsters are wrapping up their polls and posting their predictions on who will win. The polls in this graph predict Harris' win percentage, with the average in the blue line. The dots in the graph below represent individual polls conducted in the months leading up to the election. They are coloured based on their transparency_score, which is fivethirtyeight's metric for transpareny in the pollster's methodology. 
#| echo: false
#| warning: false
#| message: false

@@

@@

# Color by transparency_score
base_plot_trump +
  geom_point(aes(color = factor(numeric_grade))) +
  geom_smooth(color = "red") +
  theme(legend.position = "bottom")
```
{{< pagebreak >}}

### pollster

@@

For the sake of readability, @fig-pollster_harris & @fig-pollster_trump shows 13 an interesting bump in predictions by George Mass. This may have been an error on their part however, as it is almost immediately rectified.
```{r}
#| label: fig-pollster_harris
#| fig-cap: As election day draws close, pollsters are wrapping up their polls and posting their predictions on who will win. Each graph shows individual polls conducted in the months leading up to the election. They represent the change in prediciton for Kamala Harris winning the presidency.
#| echo: false
#| warning: false
#| message: false
#| fig-width: 5
#| fig-height: 4

polls_12 <- c("AtlasIntel", "Data for Progress", "Echelon Insights",
              "Emerson","Hart/POS", "Ipsos","Marist","Siena/NYT","Suffolk",
              "SurveyUSA","U. New Hampshire","YouGov", "Washington Post/George Mason University")

new_base_plot_kamala <- just_harris_high_quality |>
  filter(pollster %in% polls_12) |>
  ggplot(aes(x = end_date, y = pct)) +
  theme_classic() +
  labs(y = "Harris percent", x = "Date")

# Facet by pollster
new_base_plot_kamala +
  geom_point() +
  geom_smooth(color = "blue") +
  scale_y_continuous(breaks=c(0,50, 100)) +
  theme(axis.text.x =element_text(angle=45,hjust=1)) +
  facet_wrap(vars(pollster), ncol=3) 
```

```{r}
#| label: fig-pollster_trump
#| fig-cap: As election day draws close, pollsters are wrapping up their polls and posting their predictions on who will win. Each graph shows individual polls conducted in the months leading up to the election. They represent the change in prediciton for Donald Trump winning the presidency.  
#| echo: false
#| warning: false
#| message: false

new_base_plot_trump <- just_trump_high_quality |>
  filter(pollster %in% polls_12) |>
  ggplot(aes(x = end_date, y = pct)) +
  theme_classic() +
  labs(y = "Trump percent", x = "Date")

# Facet by pollster
new_base_plot_trump +
  geom_point() +
  geom_smooth(color = "red") +
  scale_y_continuous(breaks=c(0,50, 100)) +
  theme(axis.text.x =element_text(angle=45,hjust=1)) +
  facet_wrap(vars(pollster), ncol=3)
